Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-26 article.tex

The objective of the last step of our filtering procedure is to decrease the
importance of spikes that occur when there is a high global activity in the
network with respect to  spikes that occur during normal activity. Indeed, we
have conjectured that when a large part of the network is firing, the rate at
which observations are made is not high enough for being able to detect
interactions and, that it would therefore be preferrable to lower their
importance by changing appropriatly their magnitude. Additionnally, it is
well-known that neurons may also spike because of a global high activity (see
\cite{stetter2012model}). In such  context, detecting pairwise neuron
interactions from the firing activity is meaningless. As such,
the signal output by $h$ is finally applied to the following function
\begin{align}
 w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
\end{align}
which effect is to magnify the importance of spikes that occur in case of low
global activity. Note that the particular case where $\sum_{j} x^{t}_j = 0$ is
solved by setting $w(x^{t}_i) = 1$.

>>>>

The objective of the last step of our filtering procedure is to decrease the
importance of spikes that occur when there is a high global activity in the
network with respect to  spikes that occur during normal activity. Indeed, we
have conjectured that when a large part of the network is firing, the rate at
which observations are made is not high enough for being able to detect
interactions and, that it would therefore be preferrable to lower their
importance by changing appropriatly their magnitude. Additionnally, it is
well-known that neurons may also spike because of a global high activity (see
\cite{stetter2012model}). In such  context, detecting pairwise neuron
interactions from the firing activity is meaningless. As such,
the signal output by $h$ is finally applied to the following function
\begin{align}
 w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
\end{align}
that has for effect to magnify the importance of spikes that occur in case of low global activity. Note that the particular case $\sum_{j} x^{t}_j$ equals $0$ is solved by setting $w(x^{t}_i) = 1$.
